---
title: "`r params$dynamictitle`"
author: "Julianna Szabo & Xinqi Wang"
params:
  dynamictitle: 'Assignment 2: Predicting Fast-growth Firms'
  viridis_palette: viridis
output:
  pdf_document: 
  html_document:
    code_download: yes
    highlighter: null
    theme: flatly
  code_download: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction: 
In this study, we are interested in predicting fast-growth firms. In reality, only a small fraction of firms achieve the highest rate of growth. Most firms either grow fast or die slow. Therefore, it is crucial to predict that fast-growth firms now will continue to be fast-growing in the future. We will use firms' financial and attributes data in a European country from the binsnode-firms dataset. We will also build and compare different predictive models and classify them into prospective fast-growth firms and prospective non-fast-growth firms to achieve the goal. 

  
## 2. Data and Sample Design: 
The original dataset is a large panel that covers the entire period of 2005 to 2016. We first filter it down to 2010 – 2015 and focus on a cross-section of firms only in 2012. Our question would be whether they keep fast-growing in the subsequent year. 

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.show='hide'}
# Clear environment
rm(list = ls())

# Load libraries
library(tidyverse)
library(haven)
library(glmnet)
library(grid)
library(purrr)
library(margins)
library(skimr)
library(kableExtra)
library(Hmisc)
library(cowplot)
library(gmodels) 
library(lspline)
library(sandwich)
library(modelsummary)

library(rattle)
library(caret)
library(pROC)
library(ranger)
library(rpart)
library(partykit)
library(rpart.plot)
library(gridExtra)

# import data

# data_url <- "https://raw.githubusercontent.com/Julianna-szabo/DA3_Assignment_2/main/data/cs_bisnode_panel.csv?token=AREBRMDA52YMHJHLWGZLSZDADU7K4"
# data <- read_csv(file = data_url)

data <- read_csv('../Assignment_2/Data/clean/cs_bisnode_panel.csv')

data_original <- data

# drop variables with many NAs
data <- data %>%
  select(-c(COGS, finished_prod, net_dom_sales, net_exp_sales, wages)) %>%
  filter(year !=2016)

options(digits = 3)
###########################################################
# label engineering
###########################################################
# add all missing year and comp_id combinations -
# originally missing combinations will have NAs in all other columns
# data <- data %>%
#   complete(year, comp_id)

# Filter 2010 - 2015

data <- data %>% 
  filter(year >= 2011 & year <=2015)

# Sort by company id

data <- data[order(data$comp_id),]

# Size and growth
summary(data$sales) # There will be NAs, we'll drop them soon

data <- data %>%
  mutate(sales = ifelse(sales < 0, 1, sales),
         ln_sales = ifelse(sales > 0, log(sales), 0),
         sales_mil=sales/1000000,
         sales_mil_log = ifelse(sales > 0, log(sales_mil), 0))

data <- data %>%
  group_by(comp_id) %>%
  mutate(d1_sales_mil_log = sales_mil_log - Lag(sales_mil_log, 1) ) %>%
  ungroup()


# replace w 0 for new firms + add dummy to capture it
data <- data %>%
  mutate(age = (year - founded_year) %>%
           ifelse(. < 0, 0, .),
         new = as.numeric(age <= 1) %>% #  (age could be 0,1 )
           ifelse(balsheet_notfullyear == 1, 1, .),
         d1_sales_mil_log = ifelse(new == 1, 0, d1_sales_mil_log),
         new = ifelse(is.na(d1_sales_mil_log), 1, new),
         d1_sales_mil_log = ifelse(is.na(d1_sales_mil_log), 0, d1_sales_mil_log))


############################
# Find fast growing firms  #
############################

# Filter for only years 2012 and 2013

data <- data %>% 
  filter(year == 2012 | year == 2013)

# Check for missing values

count_missing_values <- function(data) {
  num_missing_values <- map_int(data, function(x) sum(is.na(x)))
  num_missing_values[num_missing_values > 0]
}
count_missing_values(data)

# Drop 

data<- filter(data, !is.na(profit_loss_year)) 
data<- filter(data, !is.na(sales)) 
data<- filter(data, !is.na(inc_bef_tax)) 


# Drop company IDs which do not have observations for both years
comp_count_check <- data %>% 
  group_by(comp_id) %>% 
  count()

missing <- comp_count_check %>% 
  filter(n<2)

data <- data[!(data$comp_id %in% (missing$comp_id)),]

rm(missing, comp_count_check)

# Create year on year column

# Columns to do year on year for
y_on_y <- c("profit_loss_year", "sales", "inc_bef_tax")

# Look at all unique values for com_id
for (i in unique(data$comp_id)) {
  # Look at all the columns to use for year on year
  for (j in y_on_y) {
    column_name <- (paste0(j, "_y_on_y"))
    # Find the row numbers
    row_2013 <- which(data$comp_id == i & data$year == 2013)
    row_2012 <- which(data$comp_id == i & data$year == 2012)
    # Create the year on year columns
    data[row_2013, column_name] <- (data[row_2013, j] - data[row_2012, j]) / data[row_2012, j] 
  }
}

#transform the data, take the 2013 rows and make them into columns, so we only left with 2012 explantory varibales
new_data_2013<-filter(data, year==2013)
new_data_2012<-filter(data, year==2012)

data <- as.data.frame(cbind(new_data_2012, new_data_2013$profit_loss_year_y_on_y, new_data_2013$sales_y_on_y, new_data_2013$inc_bef_tax_y_on_y))

data <- mutate(data, profit_loss_year_y_on_y = new_data_2013$profit_loss_year_y_on_y,
               sales_y_on_y = new_data_2013$sales_y_on_y,
               inc_bef_tax_y_on_y = new_data_2013$inc_bef_tax_y_on_y)

drops <- c('new_data_2013$profit_loss_year_y_on_y','new_data_2013$sales_y_on_y','new_data_2013$inc_bef_tax_y_on_y')

data <- data[ , !(names(data) %in% drops)]

# save it into clean file 
write.csv(data, "Data/fast_growth_workingfile_1.csv")

# data <- read_csv(file = "data/fast_growth_workingfile_1.csv")

##########################################################################
# Check the three different possible variables: sales, profit and EBIDTA

# Filter out infinates
data<- filter(data, !is.infinite(profit_loss_year_y_on_y)) 
data<- filter(data, !is.infinite(sales_y_on_y)) 
data<- filter(data, !is.infinite(inc_bef_tax_y_on_y)) 

# Filter out NAs 
data<- filter(data, !is.na(profit_loss_year_y_on_y)) 
data<- filter(data, !is.na(sales_y_on_y)) 
data<- filter(data, !is.na(inc_bef_tax_y_on_y))

glimpse(data)

##############################
# 1). Growth on sales_y_on_y:
##############################
# check growth on sales statistics
data %>% 
  summarise(
    Obs = 'sales_y_on_y',
    n = sum( !is.na( sales_y_on_y ) ),
    mean = mean(sales_y_on_y),
    first_quartile = quantile( !is.na(sales_y_on_y), 0.25),
    median   = median(sales_y_on_y),
    third_quartile = quantile(!is.na(sales_y_on_y), 0.75),
    min = min(sales_y_on_y),
    max = max(sales_y_on_y),
    sd = sd(sales_y_on_y)
  )
# from the summary statistics, we should filter out extreme variables. Let's restrict max growth on sales at 200%, and min growth
# (max loss) at -200%

# check summary statistics again:
summary_sales_growth <- data %>% 
  filter(sales_y_on_y < 2 & sales_y_on_y > -2) %>% 
  summarise(
    Obs = 'sales_y_on_y',
    n = sum( !is.na(sales_y_on_y )),
    mean = mean(sales_y_on_y),
    first_quartile = quantile(sales_y_on_y, 0.25),
    median   = median(sales_y_on_y),
    third_quartile = quantile(sales_y_on_y, 0.75),
    min = min(sales_y_on_y),
    max = max(sales_y_on_y),
    sd = sd(sales_y_on_y)
  )

count(data, sales_y_on_y > 0)

# check distribution
data %>% 
  filter(sales_y_on_y < 2 & sales_y_on_y > -2) %>% 
  ggplot(aes(x = sales_y_on_y)) +
  geom_histogram(bins = 100)


###########################################
# 2). Growth on profit_loss_year_y_on_y:
###########################################
# Distribution of profit year on year
data %>% 
  summarise(
    Obs = 'profit_loss_year_y_on_y',
    n = sum( !is.na( profit_loss_year_y_on_y ) ),
    mean = mean(profit_loss_year_y_on_y),
    first_quartile = quantile(profit_loss_year_y_on_y, 0.25),
    median   = median(profit_loss_year_y_on_y),
    third_quartile = quantile(profit_loss_year_y_on_y, 0.75),
    min = min(profit_loss_year_y_on_y),
    max = max(profit_loss_year_y_on_y),
    sd = sd(profit_loss_year_y_on_y)
  )
# from the summary statistics, we should filter out extreme variables. Let's restrict max growth on profit at 200%, and min growth
# (max loss) at -200%

# check summary statistics again:
summary_profit_growth <- data %>% 
  filter(profit_loss_year_y_on_y < 2 & profit_loss_year_y_on_y > -2) %>% 
  summarise(
    Obs = 'profit_loss_year_y_on_y',
    n = sum( !is.na( profit_loss_year_y_on_y ) ),
    mean = mean(profit_loss_year_y_on_y),
    first_quartile = quantile(profit_loss_year_y_on_y, 0.25),
    median   = median(profit_loss_year_y_on_y),
    third_quartile = quantile(profit_loss_year_y_on_y, 0.75),
    min = min(profit_loss_year_y_on_y),
    max = max(profit_loss_year_y_on_y),
    sd = sd(profit_loss_year_y_on_y)
  )

count(data, profit_loss_year_y_on_y > 0)

# check distribution
data %>% 
  filter(profit_loss_year_y_on_y < 2 & profit_loss_year_y_on_y > -2) %>% 
  ggplot(aes(x = profit_loss_year_y_on_y)) +
  geom_histogram(bins = 100)


#####################################
# 3). Growth on inc_bef_tax_y_on_y:
#####################################
# Distribution of EBIDTA year on year
data %>% 
  summarise(
    Obs = 'inc_bef_tax_y_on_y',
    n = sum( !is.na( inc_bef_tax_y_on_y ) ),
    mean = mean(inc_bef_tax_y_on_y),
    first_quartile = quantile(inc_bef_tax_y_on_y, 0.25),
    median   = median(inc_bef_tax_y_on_y),
    third_quartile = quantile(inc_bef_tax_y_on_y, 0.75),
    min = min(inc_bef_tax_y_on_y),
    max = max(inc_bef_tax_y_on_y),
    sd = sd(inc_bef_tax_y_on_y)
  )

# from the summary statistics, we should filter out extreme variables. Let's restrict max growth on profit at 200%, and min growth
# (max loss) at -200%

# check summary statistics again:
summary_EBIDTA_growth <- data %>% 
  filter(inc_bef_tax_y_on_y < 2 & inc_bef_tax_y_on_y > -2) %>% 
  summarise(
    Obs = 'inc_bef_tax_y_on_y',
    n = sum( !is.na( inc_bef_tax_y_on_y ) ),
    mean = mean(inc_bef_tax_y_on_y),
    first_quartile = quantile(inc_bef_tax_y_on_y, 0.25),
    median   = median(inc_bef_tax_y_on_y),
    third_quartile = quantile(inc_bef_tax_y_on_y, 0.75),
    min = min(inc_bef_tax_y_on_y),
    max = max(inc_bef_tax_y_on_y),
    sd = sd(inc_bef_tax_y_on_y)
  )

count(data, inc_bef_tax_y_on_y > 0)

# check distribution
data %>% 
  filter(inc_bef_tax_y_on_y < 2 & inc_bef_tax_y_on_y > -2) %>% 
  ggplot(aes(x = inc_bef_tax_y_on_y)) +
  geom_histogram(bins = 100)

# combine the 3 summary statistics together
growth_variables_summary <- summary_sales_growth %>% add_row( summary_profit_growth ) %>% add_row(summary_EBIDTA_growth)
growth_variables_summary
```

### 2.1 Label Engineering: 
The next step is to define our target variable, y, as fast-growth is not defined in the dataset. We consider several options to define a fast-growth firm. First, we decide to use 1-year growth, specifically from 2012 to 2013, to interpret and make more sense in economic terms. Next, we choose three financial variables, namely sales, profit/loss, and income before taxes, and apply this growth calculation. After cleaning and filtering out NAs and extreme variables, we report a combined summary statistic table below. It shows the total number of variables and, most importantly, the third quartile of each variable (We will talk about why the third quartile is essential later in the threshold decision phase). Sales growth gives 18909 variables, profit/loss gives 15156, and income before taxes gives 15145. We decide to pick sales growth based on the number of total variables. After confirming the growth variable, we need to create a fast-growth binary variable indicating firms who are a fast-growth with assigning them with 1. So how to pick the threshold is essential. We first try to compare them with the broader views of fast-growth firms: it is usually accepted that if a firm is growing faster than the overall economy, it should be considered fast-growing. In reality, the average European Union GDP growth for 2013 was at -0.055%. However, a substantial percentage of our data will be categorized into fast growth if using this number as the threshold. Therefore, we decide to use the third quartile of sales growth as the threshold. Any firm has a sales growth higher than 21.3% in 2013, and we will consider it a fast-growth firm. 

\begin{table}[htbp]
\centering
\caption{\bf Summary Statistics of Growth Variable Candidates}
\begin{tabular}[t]{lcccccccc}
\hline\hline
Obs & n & mean & First Quartile & Median & Third Quartile & Min & Max & SD\\
\hline
sales\_y\_on\_y & 18908 & -0.0182 & -0.293 & -0.00893 & 0.213 & -1 & 2 & 0.547 \\
\hline
profit\_loss\_year\_y\_on\_y & 15156 & -0.3285 & -0.957 & -0.43663 & 0.141 & -2 & 2 & 0.807 \\
\hline
inc\_bef\_tax\_y\_on\_y & 15145 & -0.2867 & -0.903 & -0.36816 & 0.184 & -2 & 2 & 0.810 \\
\hline
\end{tabular}
  \label{tab:shape-functions}
\end{table}


### 2.2 Sample Design 
For the sample data, we focus on the year 2012 alive firms. Like the case study, we decide to focus on the small and medium enterprise sector, captured by the firm's annual sales below 10 million euros. The reason is that fast-growth firms are usually small or medium start-ups with a lower number of sales initially, and we would like to focus on that in this study. We also decide to drop anything that is below 1000 euros. They seem to be firms that are not operating normally. As a result of our sample design, we include firms with annual sales below 10 million euros and exclude those are below 1000 euros in 2012. The total number of our cleaned sample size is 18248, and of which, 4609 of them will be fast growth in 2013. That is about 25% of the total firms. 


### 2.3 Feature Engineering  
In this process, we aim to select our predictive variables, clean and transform them into an appropriate form. We choose to use similar variables and features we used for exit prediction in the case study. Four groups are formed based on variables' attributes: size, management, financial variables and other characteristics. For the firm's characteristics, we include whether the firm has foreign management dummy, whether the firm's CEO is a female dummy, the location regions for its headquarters, age of the firm, industry categories and winsorized age and flags. Winsorized variables are generated to capture extreme values by establishing a threshold value and replacing values outside of this threshold by the threshold itself, and adding a flag variable. 

All the financial account variables should be non-negative, so we replace them with zero and add a binary variable to flag error. We also create ratios for profit/loss and balance sheet variables. The profit/loss variables are scaled by sales, whereas total assets scale balance sheet variables. 
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide', fig.show='hide'}
# We choose to use growth on sales as our growth vairbale since it gives the largest data sample and more consistant
data <- filter(data, sales_y_on_y < 2 & sales_y_on_y > -2)

# Binary variables for fast growth on SALES - target variable
data <- data %>% 
  mutate(
    fast_growth_sales = ifelse((sales_y_on_y >= 0.213), 1, 0))

# save file
write.csv(data, "Data/fast_growth_workingfile_targetchoosen.csv")


# generate status_alive; if sales larger than zero and not-NA, then firm is alive
data  <- data %>%
  mutate(status_alive = sales > 0 & !is.na(sales) %>%
           as.numeric(.))


#####################
### Sample design ##
####################
# data <- read_csv(file = "Data/Clean/fast_growth_workingfile_targetchoosen.csv")
data <- data %>%
  filter((year == 2012) & (status_alive == 1)) %>%
  # look at firms below 10m euro revenues and above 1000 euros
  filter(!(sales_mil > 10)) %>%
  filter(!(sales_mil < 0.001))


###########################################################
# Feature engineering
###########################################################

# change some industry category codes
data <- data %>%
  mutate(ind2_cat = ind2 %>%
           ifelse(. > 56, 60, .)  %>%
           ifelse(. < 26, 20, .) %>%
           ifelse(. < 55 & . > 35, 40, .) %>%
           ifelse(. == 31, 30, .) %>%
           ifelse(is.na(.), 99, .)
  )

table(data$ind2_cat)

# Firm characteristics
data <- data %>%
  mutate(age2 = age^2,
         foreign_management = as.numeric(foreign >= 0.5),
         gender_m = factor(gender, levels = c("female", "male", "mix")),
         m_region_loc = factor(region_m, levels = c("Central", "East", "West")))

###########################################################
# look at more financial variables, create ratios
###########################################################

# assets can't be negative. Change them to 0 and add a flag.
data <-data  %>%
  mutate(flag_asset_problem=ifelse(intang_assets<0 | curr_assets<0 | fixed_assets<0,1,0  ))
table(data$flag_asset_problem)

data <- data %>%
  mutate(intang_assets = ifelse(intang_assets < 0, 0, intang_assets),
         curr_assets = ifelse(curr_assets < 0, 0, curr_assets),
         fixed_assets = ifelse(fixed_assets < 0, 0, fixed_assets))

# generate total assets
data <- data %>%
  mutate(total_assets_bs = intang_assets + curr_assets + fixed_assets)
summary(data$total_assets_bs)


pl_names <- c("extra_exp","extra_inc",  "extra_profit_loss", "inventories",
              "material_exp", "personnel_exp", "inc_bef_tax", "profit_loss_year")
bs_names <- c("intang_assets", "curr_liab", "fixed_assets", "liq_assets", "curr_assets",
              "share_eq", "subscribed_cap", "tang_assets" )

# Create rations
# divide all pl_names elements by sales and create new column for it
data <- data %>%
  mutate_at(vars(pl_names), funs("pl"=./sales))

# divide all bs_names elements by total_assets_bs and create new column for it
data <- data %>%
  mutate_at(vars(bs_names), funs("bs"=ifelse(total_assets_bs == 0, 0, ./total_assets_bs)))


########################################################################
# creating flags, and winsorizing tails
########################################################################

# Variables that represent accounting items that cannot be negative (e.g. materials)
zero <-  c("extra_exp_pl", "extra_inc_pl", "inventories_pl", "material_exp_pl", "personnel_exp_pl",
           "curr_liab_bs", "fixed_assets_bs", "liq_assets_bs", "curr_assets_bs", "subscribed_cap_bs",
           "intang_assets_bs")

data <- data %>%
  mutate_at(vars(zero), funs("flag_high"= as.numeric(.> 1))) %>%
  mutate_at(vars(zero), funs(ifelse(.> 1, 1, .))) %>%
  mutate_at(vars(zero), funs("flag_error"= as.numeric(.< 0))) %>%
  mutate_at(vars(zero), funs(ifelse(.< 0, 0, .)))


# for vars that could be any, but are mostly between -1 and 1
any <-  c("extra_profit_loss_pl", "share_eq_bs", "inc_bef_tax_pl", "profit_loss_year_pl")

data <- data %>%
  mutate_at(vars(any), funs("flag_low"= as.numeric(.< -1))) %>%
  mutate_at(vars(any), funs(ifelse(.< -1, -1, .))) %>%
  mutate_at(vars(any), funs("flag_high"= as.numeric(.> 1))) %>%
  mutate_at(vars(any), funs(ifelse(.> 1, 1, .))) %>%
  mutate_at(vars(any), funs("flag_zero"= as.numeric(.== 0))) %>%
  mutate_at(vars(any), funs("quad"= .^2))


# dropping flags with no variation
variances<- data %>%
  select(contains("flag")) %>%
  apply(2, var, na.rm = TRUE) == 0

data <- data %>%
  select(-one_of(names(variances)[variances]))

########################################################################
# additional
# including some imputation
########################################################################

# CEO age
data <- data %>%
  mutate(ceo_age = year-birth_year,
         flag_low_ceo_age = as.numeric(ceo_age < 25 & !is.na(ceo_age)),
         flag_high_ceo_age = as.numeric(ceo_age > 75 & !is.na(ceo_age)),
         flag_miss_ceo_age = as.numeric(is.na(ceo_age)))

data <- data %>%
  mutate(ceo_age = ifelse(ceo_age < 25, 25, ceo_age) %>%
           ifelse(. > 75, 75, .) %>%
           ifelse(is.na(.), mean(., na.rm = TRUE), .),
         ceo_young = as.numeric(ceo_age < 40))

# number emp, very noisy measure
data <- data %>%
  mutate(labor_avg_mod = ifelse(is.na(labor_avg), mean(labor_avg, na.rm = TRUE), labor_avg),
         flag_miss_labor_avg = as.numeric(is.na(labor_avg)))

summary(data$labor_avg)
summary(data$labor_avg_mod)

data <- data %>%
  select(-labor_avg)

# create factors
data <- data %>%
  mutate(urban_m = factor(urban_m, levels = c(1,2,3)),
         ind2_cat = factor(ind2_cat, levels = sort(unique(data$ind2_cat))))

data <- data %>%
  mutate(fast_growth_sales_f = factor(fast_growth_sales, levels = c(0,1)) %>%
           recode(., `0` = 'no_fast_growth', `1` = "fast_growth"))

```























## Appendix
```{r, message = F, echo = FALSE, warning=FALSE, fig.height= 3, fig.width= 8,  fig.align='center'}
########################################################################
# sales CHECK
########################################################################

data <- data %>%
  mutate(sales_mil_log_sq=sales_mil_log^2)


sales_sum_plot <- ggplot(data = data, aes(x=sales_mil_log, y=as.numeric(fast_growth_sales))) +
  geom_point(size=2,  shape=20, stroke=2, fill="blue", color="blue") +
  geom_smooth(method = "lm", formula = y ~ poly(x,2), color='orange', se = F, size=1)+
  geom_smooth(method="loess", se=F, colour='darkgreen', size=1.5, span=0.9) +
  labs(x = "sales_mil_log",y = "fast_growth_firms") +
  theme_light() +
  theme(axis.text.x=element_text(size=6,face = "plain")) +
  theme(axis.text.y=element_text(size=6,face = "plain")) +
  theme(axis.title.x=element_text(size=6, vjust=0, face = "plain")) +
  theme(axis.title.y=element_text(size=6,vjust=1.25, face = "plain"))


ols_s <- lm(fast_growth_sales~sales_mil_log+sales_mil_log_sq,
            data = data)
# summary(ols_s)

########################################################################
# sales change CHECK
########################################################################
# Note: graphs not in book

# lowess
# Hmisc::describe(data$d1_sales_mil_log) # no missing

d1sale_1<-ggplot(data = data, aes(x=d1_sales_mil_log, y=as.numeric(fast_growth_sales))) +
  geom_point(size=0.1,  shape=20, stroke=2, fill='orange', color='orange') +
  geom_smooth(method="loess", se=F, colour='darkgreen', size=1.5, span=0.9) +
  labs(x = "Growth rate (Diff of ln sales)",y = "fast_growth_firms") +
  theme_light() +
  theme(axis.text.x=element_text(size=6,face = "plain")) +
  theme(axis.text.y=element_text(size=6,face = "plain")) +
  theme(axis.title.x=element_text(size=6, vjust=0, face = "plain")) +
  theme(axis.title.y=element_text(size=6,vjust=1.25, face = "plain")) +
  scale_x_continuous(limits = c(-6,10), breaks = seq(-5,10, 5))

grid.arrange(sales_sum_plot,d1sale_1, ncol = 2)
# generate variables ---------------------------------------------------

data <- data %>%
  mutate(flag_low_d1_sales_mil_log = ifelse(d1_sales_mil_log < -1.5, 1, 0),
         flag_high_d1_sales_mil_log = ifelse(d1_sales_mil_log > 1.5, 1, 0),
         d1_sales_mil_log_mod = ifelse(d1_sales_mil_log < -1.5, -1.5,
                                       ifelse(d1_sales_mil_log > 1.5, 1.5, d1_sales_mil_log)),
         d1_sales_mil_log_mod_sq = d1_sales_mil_log_mod^2
  )

# no more imputation, drop obs if key vars missing
data <- data %>%
  filter(!is.na(liq_assets_bs),!is.na(foreign), !is.na(ind))

# drop missing
data <- data %>%
  filter(!is.na(age),!is.na(foreign), !is.na(material_exp_pl), !is.na(m_region_loc))
# Hmisc::describe(data$age)

# drop unused factor levels
data <- data %>%
  mutate_at(vars(colnames(data)[sapply(data, is.factor)]), funs(fct_drop))

d1sale_2<-ggplot(data = data, aes(x=d1_sales_mil_log_mod, y=as.numeric(fast_growth_sales))) +
  geom_point(size=0.1,  shape=20, stroke=2, fill='orange', color='orange') +
  geom_smooth(method="loess", se=F, colour='darkgreen', size=1.5, span=0.9) +
  labs(x = "Growth rate (Diff of ln sales)",y = "fast_growth_firms") +
  theme_light() +
  theme(axis.text.x=element_text(size=6,face = "plain")) +
  theme(axis.text.y=element_text(size=6,face = "plain")) +
  theme(axis.title.x=element_text(size=6, vjust=0, face = "plain")) +
  theme(axis.title.y=element_text(size=6,vjust=1.25, face = "plain")) +
  scale_x_continuous(limits = c(-1.5,1.5), breaks = seq(-1.5,1.5, 0.5))

d1sale_3<-ggplot(data = data, aes(x=d1_sales_mil_log, y=d1_sales_mil_log_mod)) +
  geom_point(size=0.1,  shape=20, stroke=2, fill='orange', color='orange') +
  labs(x = "Growth rate (Diff of ln sales) (original)",y = "Growth rate (Diff of ln sales) (winsorized)") +
  theme_light() +
  theme(axis.text.x=element_text(size=6,face = "plain")) +
  theme(axis.text.y=element_text(size=6,face = "plain")) +
  theme(axis.title.x=element_text(size=6, vjust=0, face = "plain")) +
  theme(axis.title.y=element_text(size=6,vjust=1.25, face = "plain")) +
  scale_x_continuous(limits = c(-5,5), breaks = seq(-5,5, 1)) +
  scale_y_continuous(limits = c(-3,3), breaks = seq(-3,3, 1))

grid.arrange(d1sale_2,d1sale_3, ncol = 2)
```


